Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-07-29 paper/comoving-followup.tex
refs

Other speculative explanations for this pair stem from the possibility that it
is the outcome of an interaction between even more stars.
For example, an interaction between two wide binaries could result in an
exchange of members, a hardening of one resulting binary, and a widening of the
other binary (see, e.g., \citealt{Nathan??}).
Or, the initial system could have been an unstable three-body system that
resulted in a tight inner binary and a wide outer binary;
if the inner binary were close enough, it could have merged and formed a blue
straggler star (e.g., \citealt{??}), leaving the wide binary untouched.

@@

>>>>

Other speculative explanations for this pair stem from the possibility that it
is the outcome of an interaction between even more stars.
For example, an interaction between two wide binaries could result in an
exchange of members, a hardening of one resulting binary, and a widening of the
other binary (see, e.g., \citealt{Leigh:2016}).
Or, the initial system could have been an unstable three-body system that
resulted in a tight inner binary and a wide outer binary;
if the inner binary were close enough, it could have merged and formed a blue
straggler star (e.g., \citealt{Naoz:2014}), leaving the wide binary untouched.

@@

\todo{Reiterate that monotonically decreasing separation distribution is too
simple}
